---
title: "Schema boards: Analyzing everything"
output:
  html_document:
    number_sections: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Setup: load data, define variables, etc

```{r load-data-define-variables}

rm(list=ls())

source('./scripts/utils/load_all_libraries.R')

qc_filter <- T

plot_normality <- T
plot_mouse_clicks <- F
plot_fits_near_far <- F

source('./scripts/utils/load_transform_data.R')

qc_table <- import('./results/qc_check_sheets/qc_table.csv')

if (qc_filter){
        
        qc_pass_ptp <- qc_table %>%
                filter(!qc_fail_overall) %>%
                select(ptp) %>% .[[1]]
        
        
        data_summary <- data_summary %>%
                filter(ptp %in% qc_pass_ptp)
        long_data <- long_data %>%
                filter(ptp %in% qc_pass_ptp) 
        mean_by_rep_long_all_types <- mean_by_rep_long_all_types %>%
                filter(ptp %in% qc_pass_ptp)
        
}

## BF test against 0 
reportBF = function(x, digits){
        round(as.numeric(as.vector(x)), digits)
}

```

# Normality checks

## Block 2

```{r block-2-normality-checks}
if (plot_normality){
       # Density plot
data_summary %>%
        ggplot(aes(x=block_2_mouse_error_mean,
                   y = ..density..)) +
        geom_histogram() +
        geom_density(lwd = 1,
                     color = 'red') +
        facet_wrap(~hidden_pa_img_type) +
        ggtitle('Block 2, RAW: Histogram and Density')

# QQ Plot

data_summary %>%
        ggqqplot(x = 'block_2_mouse_error_mean') +
        ggtitle('Block 2, RAW: QQ Plots') +
        facet_wrap(~hidden_pa_img_type) 
}


```

```{r log-transformations}
if (plot_normality){
        
    # Density plot
data_summary %>%
        mutate(block_2_mouse_error_mean_LOG = log(block_2_mouse_error_mean)) %>%
        ggplot(aes(x=block_2_mouse_error_mean_LOG,
                   y = ..density..)) +
        geom_histogram() +
        geom_density(lwd = 1,
                     color = 'red') +
        facet_wrap(~hidden_pa_img_type) +
        ggtitle('Block 2, LOG: Histogram and Density')

# QQ Plot

data_summary %>%
        mutate(block_2_mouse_error_mean_LOG = log(block_2_mouse_error_mean)) %>%
        ggqqplot(x = 'block_2_mouse_error_mean_LOG') +
        ggtitle('Block 2, LOG: QQ Plots') +
        facet_wrap(~hidden_pa_img_type)

data_summary <- data_summary %>%
        mutate(block_2_mouse_error_mean_LOG = log(block_2_mouse_error_mean))    
        
}


```

# Plot mouse clicks

```{r mouse-heat-plots, fig.width=15, fig.height=20}
if (plot_mouse_clicks){
      long_data %>%
        filter(block == 2) %>%
        droplevels() %>%
        ggplot(aes(mouse_clientX - left_offset,mouse_clientY - top_offset)) +
        geom_point(alpha=0.3) +
        geom_point(aes(pa_center_x - left_offset,pa_center_y - top_offset),
                   color='red',
                   size=2) +
        # geom_density_2d_filled(alpha = 0.3) +
        facet_grid(ptp~condition) +
        ggtitle('block 2: Mouse click locations relative to PA')  
        
        
}


```

# Learning curve plots

## All data, each condition

```{r raw-learning-curves-and-fits, fig.width=13, fig.height=40}


# Plot the fits
fig_each_ptp <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type == 'all_pa',
               border_dist_closest == 'all') %>%
        droplevels() %>%        
        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=mouse_error_mean)) +
        geom_vline(xintercept = 4.5, linetype = 'dashed') +
        
        geom_point(alpha=0.5) +
        geom_line(alpha=0.5) +        
        
        
        # Add the y_hat two parameters
        geom_line(aes(x=hidden_pa_img_row_number_across_blocks,
                      y=y_hat_two_param),
                  size=1,
                  color='red',
                  linetype = 'twodash') +           
        
        # Add the y_hat three parameters
        geom_line(aes(x=hidden_pa_img_row_number_across_blocks,
                      y=y_hat_three_param),
                  size=1,
                  color='blue',
                  linetype = 'longdash') +                   
        
        geom_text(data=filter(
                data_summary,
                hidden_pa_img_type == 'all_pa',
                ),
                aes(x=4.5,
                    y=250,
                    label = paste('int=',
                                  as.character(round(intercept_two_param,2)),
                                  ' ',
                                  'rate=',
                                  as.character(round(learning_rate_two_param,2)),
                                  seq='')),
                color = 'red') +
        geom_text(data=filter(
                data_summary,
                hidden_pa_img_type == 'all_pa',
                ),
                aes(x=4.5,
                    y=200,
                    label = paste('int=',
                                  as.character(round(intercept_three_param,2)),
                                  ' ',
                                  'rate=',
                                  as.character(round(learning_rate_three_param,2)),
                                  seq='')),
                color = 'blue') +        
        
        
        facet_grid(ptp~condition) +
        ggtitle(paste('Mouse euclidean distance',sep='')) +
        xlab('Image repetition') +
        ylab('Mouse euclidean distance ') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        scale_y_continuous(breaks=seq(0,250,50)) +
        theme(legend.position = '') +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

print(fig_each_ptp)

```

## All data, overlaid

```{r learning-curves-across-part, fig.width=7, fig.height=6}

# Plot the fits
fig_each_ptp <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type == 'all_pa',
               border_dist_closest == 'all') %>%
        droplevels() %>%                
        group_by(condition,
                 hidden_pa_img_row_number_across_blocks) %>%
        summarise(n = n(),
                  mouse_error_mean_across_ptp = mean(mouse_error_mean,na.rm = T),
                  mouse_error_sd_across_ptp = sd(mouse_error_mean, na.rm = T),
                  sem = mouse_error_sd_across_ptp/sqrt(n),
                  upper_95_ci = mouse_error_mean_across_ptp + qt(0.975,df = n-1)*sem,
                  lower_95_ci = mouse_error_mean_across_ptp - qt(0.975,df = n-1)*sem) %>% 
        ungroup() %>% 
        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=mouse_error_mean_across_ptp,
                   color=condition)) +
        geom_point(size=2) +
        geom_line(size=1) +
        # geom_ribbon(aes(ymin = lower_95_ci, 
        #                 ymax = upper_95_ci,
        #                 group=condition,
        #                 color=condition),
        #             alpha = 0.1) +

        # facet_grid(~condition) +
        ggtitle(paste('Mouse euclidean distance; Across participants',sep='')) +
        xlab('Image repetition') +
        ylab('Mouse euclidean distance ') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        scale_y_continuous(breaks=seq(0,200,25)) +  
        coord_cartesian(ylim = c(0,200)) +
        # theme(legend.position = 'top') +
        geom_vline(xintercept = 4.5, linetype = 'dashed') +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())        



print(fig_each_ptp)


```

## Near vs far

```{r landmark-raw-learning-curves-and-fits, fig.width=18, fig.height=60}
if (plot_fits_near_far){
        # For mouse euclidean distance
        
        fig_each_ptp_lm <- mean_by_rep_long_all_types %>%
                filter(hidden_pa_img_type %in% c('near','far'),
                       !condition %in% c('random_locations','no_schema'),
                       border_dist_closest == 'all'
                       ) %>%
                droplevels() %>%
                
                ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                           y=mouse_error_mean,
                           group=hidden_pa_img_type,
                           color=hidden_pa_img_type)) +
                geom_point(size=2) +
                geom_line(size=0.5) +
        
                # Add the y_hat learning and intercept
                geom_line(aes(x=hidden_pa_img_row_number_across_blocks,
                              y=y_hat_two_param),
                          size=0.8,
                          # color='blue',
                          linetype = 'twodash') +
                
                # Add the y_hat learning and intercept
                geom_line(aes(x=hidden_pa_img_row_number_across_blocks,
                              y=y_hat_three_param),
                          size=0.8,
                          # color='blue',
                          linetype = 'longdash') +
                
                
                facet_grid(ptp~condition) +
                ggtitle('Mouse euclidean distance') +
                xlab('Image repetition') +
                ylab('Mouse euclidean distance') +
                scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
                scale_y_continuous(breaks=seq(0,250,50)) +
        
                # theme(legend.position = 'top') +
                geom_vline(xintercept = 4.5, linetype = 'dashed') +
                # theme(legend.position = '') +
                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())        
        
        
        print(fig_each_ptp_lm)
}

```

## Near vs far, across-participants

```{r landmark-raw-learning-curves-and-fits-overlaid, fig.width=8, fig.height=5}

# For mouse euclidean distance

fig_each_ptp_lm <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type %in% c('near','far'),
               !condition %in% c('random_locations','no_schema'),
               border_dist_closest == 'all'
               ) %>%
        droplevels() %>%
        
        group_by(condition,
                 hidden_pa_img_type,
                 hidden_pa_img_row_number_across_blocks) %>%
        summarise(n = n(),
                  mouse_error_mean_across_ptp = mean(mouse_error_mean,na.rm = T)) %>% 
        ungroup() %>%
        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=mouse_error_mean_across_ptp,
                   color=condition,
                   linetype=hidden_pa_img_type)) +        
        
        geom_point(size=1) +
        geom_line(size=0.5) +

        ggtitle('Mouse euclidean distance') +
        xlab('Image repetition') +
        ylab('Mouse euclidean distance') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        scale_y_continuous(breaks=seq(0,250,50)) +

        # theme(legend.position = 'top') +
        geom_vline(xintercept = 4.5, linetype = 'dashed') +
        # theme(legend.position = '') +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())        


print(fig_each_ptp_lm)


```


## Near vs far difference across trials:

```{r near-far-diff-across-reps, fig.width=10, fig.height=7}

fig <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type %in% c('near','far'),
               !condition %in% c('random_locations','no_schema'),
               border_dist_closest == 'all'
               ) %>%
        droplevels() %>%

        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition,
                                hidden_pa_img_row_number_across_blocks),
                    names_from = hidden_pa_img_type,
                    values_from = mouse_error_mean) %>% 
        mutate(far_minus_near = far - near) %>% 
        
        
        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=far_minus_near,
                   color=condition,
                   group=condition)) +        
        
        geom_point(size=1) +
        geom_line(size=0.5) +

        facet_wrap(~ptp) +
        ggtitle('Mouse euclidean distance') +
        xlab('Image repetition') +
        ylab('Mouse euclidean distance') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        scale_y_continuous(breaks=seq(0,250,50)) +

        # theme(legend.position = 'top') +
        geom_vline(xintercept = 4.5, linetype = 'dashed') +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        # theme(legend.position = '') +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())        


print(fig)


```

## Near vs far diff, across participants:

```{r near-far-diff-across-reps-overlaid, fig.width=7, fig.height=5}

fig <- mean_by_rep_long_all_types %>%
        filter(hidden_pa_img_type %in% c('near','far'),
               !condition %in% c('random_locations','no_schema'),
               border_dist_closest == 'all'
               ) %>%
        droplevels() %>%

        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition,
                                hidden_pa_img_row_number_across_blocks),
                    names_from = hidden_pa_img_type,
                    values_from = mouse_error_mean) %>% 
        mutate(far_minus_near = far - near) %>% 
        
        group_by(condition,
                 hidden_pa_img_row_number_across_blocks) %>%
        summarise(n = n(),
                  far_minus_near_mean_across_ptp = mean(far_minus_near,na.rm = T)) %>% 
        ungroup() %>%

        ggplot(aes(x=hidden_pa_img_row_number_across_blocks,
                   y=far_minus_near_mean_across_ptp,
                   color=condition,
                   group=condition)) +        
        
        geom_point(size=1) +
        geom_line(size=0.5) +

        ggtitle('Far minus Near') +
        xlab('Image repetition') +
        ylab('Far minus Near') +
        scale_x_continuous(breaks=c(1,2,3,4,5,6,7,8)) +
        scale_y_continuous(breaks=seq(-100,100,10)) +

        # theme(legend.position = 'top') +
        geom_vline(xintercept = 4.5, linetype = 'dashed') +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        # theme(legend.position = '') +
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())        


print(fig)


```

# Learning parameter estimate plots:

```{r plot-learning-parameter-estimates-two-param, fig.width=14, fig.height=5}

# Two parameter model learning rates
data_summary %>%
        # filter(hidden_pa_img_type == 'all_pa') %>%
        ggplot(aes(x=condition,
                   y=learning_rate_two_param,
                   fill=condition)) +
        geom_violin(alpha = 0.3) +
        geom_boxplot(outlier.shape = '',
                     width = 0.2,
                     fatten = 3) +
        geom_point(alpha = 0.2) +
        geom_line(aes(group = ptp),
                  alpha = 0.2) +
        stat_summary(fun = 'mean',
                     color = 'red',
                     size = 1) +
        facet_wrap(~hidden_pa_img_type) +
        ggtitle('Two parameter model: Learning rates')

# Two parameter model, intercepts
data_summary %>%
        # filter(hidden_pa_img_type == 'all_pa') %>%
        ggplot(aes(x=condition,
                   y=intercept_two_param,
                   fill=condition)) +
        geom_violin(alpha = 0.3) +
        geom_boxplot(outlier.shape = '',
                     width = 0.2,
                     fatten = 3) +
        geom_point(alpha = 0.2) +
        geom_line(aes(group = ptp),
                  alpha = 0.2) +
        stat_summary(fun = 'mean',
                     color = 'red',
                     size = 1) +
        facet_wrap(~hidden_pa_img_type) +
        ggtitle('Two parameter model: intercepts')

# Near - Far difference in learning rates
data_summary %>%
        filter(hidden_pa_img_type != 'all_pa') %>%
        droplevels() %>%
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition),
                    values_from = learning_rate_two_param,
                    names_from = hidden_pa_img_type) %>% 
        mutate(far_minus_near = far - near) %>%
        ggplot(aes(x=condition,
                   y=far_minus_near,
                   fill=condition)) +
        geom_violin(alpha = 0.3) +
        geom_boxplot(outlier.shape = '',
                     width = 0.2,
                     fatten = 3) +
        geom_point(alpha = 0.2) +
        geom_line(aes(group = ptp),
                  alpha = 0.2) +
        stat_summary(fun = 'mean',
                     color = 'red',
                     size = 1) +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        ggtitle('Two parameter model: Far-Near learning rate')

```

```{r plot-learning-parameter-estimates-three-param, fig.width=14, fig.height=5}

# Three parameter model learning rates
data_summary %>%
        ggplot(aes(x=condition,
                   y=learning_rate_three_param,
                   fill=condition)) +
        geom_violin(alpha = 0.3) +
        geom_boxplot(outlier.shape = '',
                     width = 0.2,
                     fatten = 3) +
        geom_point(alpha = 0.2) +
        geom_line(aes(group = ptp),
                  alpha = 0.2) +
        stat_summary(fun = 'mean',
                     color = 'red',
                     size = 1) +
        facet_wrap(~hidden_pa_img_type) +
        ggtitle('Three parameter model: Learning rates')

# Three parameter model, intercepts
data_summary %>%
        ggplot(aes(x=condition,
                   y=intercept_three_param,
                   fill=condition)) +
        geom_violin(alpha = 0.3) +
        geom_boxplot(outlier.shape = '',
                     width = 0.2,
                     fatten = 3) +
        geom_point(alpha = 0.2) +
        geom_line(aes(group = ptp),
                  alpha = 0.2) +
        stat_summary(fun = 'mean',
                     color = 'red',
                     size = 1) +
        facet_wrap(~hidden_pa_img_type) +
        ggtitle('Three parameter model: intercepts')

# Three parameter model, asymptote
data_summary %>%
        ggplot(aes(x=condition,
                   y=asymptote_three_param,
                   fill=condition)) +
        geom_violin(alpha = 0.3) +
        geom_boxplot(outlier.shape = '',
                     width = 0.2,
                     fatten = 3) +
        geom_point(alpha = 0.2) +
        geom_line(aes(group = ptp),
                  alpha = 0.2) +
        stat_summary(fun = 'mean',
                     color = 'red',
                     size = 1) +
        facet_wrap(~hidden_pa_img_type) +
        ggtitle('Three parameter model: asymptotes')

# Near - Far difference in learning rates
data_summary %>%
        filter(hidden_pa_img_type != 'all_pa') %>%
        droplevels() %>%
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition),
                    values_from = learning_rate_three_param,
                    names_from = hidden_pa_img_type) %>% 
        mutate(far_minus_near = far - near) %>%
        ggplot(aes(x=condition,
                   y=far_minus_near,
                   fill=condition)) +
        geom_violin(alpha = 0.3) +
        geom_boxplot(outlier.shape = '',
                     width = 0.2,
                     fatten = 3) +
        geom_point(alpha = 0.2) +
        geom_line(aes(group = ptp),
                  alpha = 0.2) +
        stat_summary(fun = 'mean',
                     color = 'red',
                     size = 1) +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        ggtitle('Three parameter model: Far-Near learning rate')

```




# Block 2 mean performance:

## Compare conditions, across PAs:

```{r block-2-conditions, fig.width=7}

data_summary %>%
        filter(hidden_pa_img_type == 'all_pa') %>%
        droplevels() %>%
        ggplot(aes(x=condition,
                   y=block_2_mouse_error_mean,
                   fill=condition)) +
        geom_violin(alpha = 0.2) +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        geom_point(alpha = 0.2) +
        # geom_jitter(height = 0,
        #             width = 0.06,
        #             alpha = 0.3) +
        geom_line(aes(group=ptp),
                  alpha = 0.1) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('Block 2, comparing conditions') +
        ylab('Block 2 error') + 
        xlab('') +
        theme(legend.position = '')

```

```{r block-2-LOG-conditions}

data_summary %>%
        filter(hidden_pa_img_type == 'all_pa') %>%
        droplevels() %>%
        
        ggplot(aes(x=condition,
                   y=block_2_mouse_error_mean_LOG)) +
        geom_violin() +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        geom_jitter(height = 0,
                    width = 0.06,
                    alpha = 0.3) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('Block 2 LOG, comparing conditions')

```



## Near vs Far within each condition:

```{r block-2-conditions-near-far, fig.width=7}

data_summary %>%
        filter(hidden_pa_img_type != 'all_pa') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition),
                    names_from = hidden_pa_img_type,
                    values_from = block_2_mouse_error_mean) %>% 
        mutate(far_minus_near = far - near) %>%
        
        ggplot(aes(x=condition,
                   y=far_minus_near,
                   fill=condition)) +
        geom_violin(alpha = 0.2) +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        # geom_jitter(height = 0,
        #             width = 0.06,
        #             alpha = 0.3) +
        geom_line(aes(group=ptp),
                  alpha = 0.1) +
        geom_point(alpha = 0.2) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('Block 2, comparing conditions, Far-Near') +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        theme(legend.position = '') +
        ylab('Far minus Near') +
        xlab('')

```

```{r block-2-LOG-conditions-near-far}

data_summary %>%
        filter(hidden_pa_img_type != 'all_pa') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition),
                    names_from = hidden_pa_img_type,
                    values_from = block_2_mouse_error_mean_LOG) %>% 
        mutate(far_minus_near = far - near) %>%
        
        ggplot(aes(x=condition,
                   y=far_minus_near)) +
        geom_violin() +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        geom_jitter(height = 0,
                    width = 0.06,
                    alpha = 0.3) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('Block 2 LOG, comparing conditions, Far-Near') +
        geom_hline(yintercept = 0, linetype = 'dashed')

```

### Bayes Factor

```{r bayes-analysis-schema-c-far-vs-near}

data_for_bf_1 <- data_summary %>%
        filter(hidden_pa_img_type != 'all_pa') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition),
                    names_from = hidden_pa_img_type,
                    values_from = block_2_mouse_error_mean) %>% 
        mutate(far_minus_near = far - near) %>%
        select(far_minus_near) %>% .[[1]]


null_interval <- c(0,Inf)

bf_1 <- reportBF(ttestBF(
        data_for_bf_1,
        nullInterval = null_interval
)[1],4)

```

```{r bayes-analysis-schema-c-far-vs-near-LOG}

data_for_bf_1_LOG <- data_summary %>%
        filter(hidden_pa_img_type != 'all_pa') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition),
                    names_from = hidden_pa_img_type,
                    values_from = block_2_mouse_error_mean_LOG) %>% 
        mutate(far_minus_near = far - near) %>%
        select(far_minus_near) %>% .[[1]]


null_interval <- c(0,Inf)

bf_1_LOG <- reportBF(ttestBF(
        data_for_bf_1_LOG,
        nullInterval = null_interval
)[1],4)

```


# Near PAs: schema-C vs schema-l

## Plot:

```{r near-pa-schema-c-vs-schema-l, fig.width=3, fig.height=4}

data_summary %>%
        filter(hidden_pa_img_type == 'near') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                hidden_pa_img_type),
                    names_from = condition,
                    values_from = block_2_mouse_error_mean) %>% 
        mutate(schema_c_minus_schema_l = schema_c - schema_l) %>% 
        
        ggplot(aes(x='difference',
                   y=schema_c_minus_schema_l)) +
        geom_violin() +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        geom_jitter(height = 0,
                    width = 0.06,
                    alpha = 0.3) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('Block 2, Near-PA, schema-c vs schema-l') +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        ylab('Schema-C minus Schema-L') +
        xlab('')

```

```{r near-pa-schema-c-vs-schema-l-LOG, fig.width=3, fig.height=4}

data_summary %>%
        filter(hidden_pa_img_type == 'near') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                hidden_pa_img_type),
                    names_from = condition,
                    values_from = block_2_mouse_error_mean_LOG) %>% 
        mutate(schema_c_minus_schema_l = schema_c - schema_l) %>% 
        
        ggplot(aes(x='difference',
                   y=schema_c_minus_schema_l)) +
        geom_violin() +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        geom_jitter(height = 0,
                    width = 0.06,
                    alpha = 0.3) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('Block 2 LOG, Near-PA, schema-c vs schema-l') +
        geom_hline(yintercept = 0, linetype = 'dashed')

```

## Bayes Factor

```{r bf-analysis-near-schema-c-vs-schema-l}

data_for_bf_2 <- data_summary %>%
        filter(hidden_pa_img_type == 'near') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                hidden_pa_img_type),
                    names_from = condition,
                    values_from = block_2_mouse_error_mean) %>% 
        mutate(schema_c_minus_schema_l = schema_c - schema_l) %>% 
        select(schema_c_minus_schema_l) %>% .[[1]]


null_interval <- c(0,Inf)

bf_2 <- reportBF(ttestBF(
        data_for_bf_2,
        nullInterval = null_interval
)[1],4)

```

# Near PAs: schema-C vs schema-IC

## Plot:

```{r near-pa-schema-c-vs-schema-ic, fig.width=3, fig.height=4}

data_summary %>%
        filter(hidden_pa_img_type == 'near') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                hidden_pa_img_type),
                    names_from = condition,
                    values_from = block_2_mouse_error_mean) %>% 
        mutate(schema_c_minus_schema_ic = schema_c - schema_ic) %>% 
        
        ggplot(aes(x='difference',
                   y=schema_c_minus_schema_ic)) +
        geom_violin() +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        geom_jitter(height = 0,
                    width = 0.06,
                    alpha = 0.3) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('Block 2, Near-PA, schema-c vs schema-ic') +
        geom_hline(yintercept = 0, linetype = 'dashed') +
        ylab('Schema-C minus Schema-IC') +
        xlab('')

```

## Bayes Factor

```{r bf-analysis-near-schema-c-vs-schema-ic}

data_for_bf_3 <- data_summary %>%
        filter(hidden_pa_img_type == 'near') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                hidden_pa_img_type),
                    names_from = condition,
                    values_from = block_2_mouse_error_mean) %>% 
        mutate(schema_c_minus_schema_ic = schema_c - schema_ic) %>% 
        select(schema_c_minus_schema_ic) %>% .[[1]]


null_interval <- c(0,Inf)

bf_3 <- reportBF(ttestBF(
        data_for_bf_3,
        nullInterval = null_interval
)[1],4)

```

```{r bf-analysis-near-schema-c-vs-schema-l-LOG}

data_for_bf_2_LOG <- data_summary %>%
        filter(hidden_pa_img_type == 'near') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                hidden_pa_img_type),
                    names_from = condition,
                    values_from = block_2_mouse_error_mean_LOG) %>% 
        mutate(schema_c_minus_schema_l = schema_c - schema_l) %>% 
        select(schema_c_minus_schema_l) %>% .[[1]]


null_interval <- c(0,Inf)

bf_2_LOG <- reportBF(ttestBF(
        data_for_bf_2_LOG,
        nullInterval = null_interval
)[1],4)

```

# Reaction times 

## Comparing conditions 

```{r rt-diff-conditions}

data_summary %>%
        filter(hidden_pa_img_type == 'all_pa') %>%
        droplevels() %>%
        
        ggplot(aes(x=condition,
                   y=block_2_rt_mean)) +
        geom_violin() +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        geom_jitter(height = 0,
                    width = 0.06,
                    alpha = 0.3) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('Block 2 RT, comparing conditions')

```

```{r rt-conditions-near-far}

data_summary %>%
        filter(hidden_pa_img_type != 'all_pa') %>%
        droplevels() %>%
        
        pivot_wider(id_cols = c(ptp,
                                counterbalancing,
                                condition),
                    names_from = hidden_pa_img_type,
                    values_from = block_2_rt_mean) %>% 
        mutate(far_minus_near = far - near) %>%
        
        ggplot(aes(x=condition,
                   y=far_minus_near)) +
        geom_violin() +
        geom_boxplot(width=0.1,
                     fatten=4,
                     outlier.shape = '') +
        geom_jitter(height = 0,
                    width = 0.06,
                    alpha = 0.3) +
        stat_summary(fun=mean,
                     color='red',
                     size=1) +
        ggtitle('Block 2 RT, comparing conditions, Far-Near') +
        geom_hline(yintercept = 0, linetype = 'dashed')

```

